---
title: "Assignment_7"
author: "The R Squad"
date: "December 21, 2017"
output: html_document
---

##Remove special characters, padding (the white space before and after the text) from Street 1 and Street 2 variables. Make sure the first letters of street names are capitalized and the street denominations are following the same standard (for example, all streets are indicated as str, avenues as ave, etc.

```{r Removes Special Characters, echo=TRUE}
#This code will Remove special characters, padding (the white space before and after the text) 
#from Street 1 and Street 2 variables
data$Street = gsub("[^A-Za-z ]", " ",data$Street)
data$Street = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data$Street, perl=TRUE)
data$Street

data$`Street 2` = gsub("[^A-Za-z ]", " ", data$`Street 2`)
data$`Street 2` = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data$`Street 2`, perl=TRUE)
data$`Street 2` 

data$Street = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data$Street, perl=TRUE)
data$`Street 2` =  gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data$`Street 2`, perl=TRUE)

```

```{r}
# This Code will Make sure the first letters of street names are capitalized and the street #denominations are following the same standard (for example, all streets are indicated as #âstr.â,avenues 

patterns     <- c("Lane", "Road", "Avenue", "Green", "Hospital", "Village", "Center", "Drive", "Circle", "Park","Street")
replacements <- c("Lan.",  "Rd.", "Ave.", "Gr.","Hosp.","Vil.","Ctr.", "Dr.", "Cr.","Pk.","Str.")

data$Street = gsubfn("\\b\\w+\\b", as.list(setNames(replacements, patterns)), data$Street)
data$`Street 2` =  gsubfn("\\b\\w+\\b", as.list(setNames(replacements, patterns)), data$`Street 2`)


```
#If the value in Street 2 duplicates the value in Street 1, remove the value in Street 2

```{r remove duplicates, echo=TRUE}

#  If the value in Street 2 duplicates the value in Street 1, 
# this code will remove the value in Street 2


i = 1

while(i < nrow(data)) 
{
  if(data$Street[i] == data$`Street 2` [i]) 
  {
    data$`Street 2` [i] = ""
  }
  i=i+1
}



```
